Efficient Parallelization of Sparse Representation for Face Recognition

### 2010-10-20 paper/main.tex
Working on introduction.  Added some pseudocode.

\begin{abstract}
Abstract
\end{abstract}

@@

@@

\section{Characteristics of the ALM Algorithm}
Describe the two variants of the ALM algorithm
Show Pseudocode for one variant
\subsection{Computational Complexity}
The Matrix-vector computions are O($mn$), and the vector-vector operations are O($m$), 
in terms of both computation cost and memory-bandwidth.
Therefore, assuming the iterative solver always takes a constant number of iterations,
the computational complexity of the overall algorithm is linear in the problem size.

@@

cuda cores, SIMD width, scheduling restrictions, bandwidth

@@

>>>>

\begin{abstract}

\end{abstract}

@@

Significant strides have been made in automatic face recognition by re-casting
it as a sparse representation problem.  This core of this algorithm consists of
stacking the test image into a vector $\y$, stacking the training images for
all of the users into the columns of a matrix $A$, and solving the following
minimization problem:
\begin{equation}
\min_{\x, \e} \| \x \|_1 + \|\e\|_1 \quad \subj \quad \y = A \x + \e.
\end{equation}
This optimization promotes a solution that is sparse both in $\x$ and $\e$. 
%The solution we are looking for should be sparse in $\x$ because

@@

For iterative alignment, we need to perform the following optimization problem:
\begin{equation}
\min_{\x, \e} \|\e\|_1 \quad \subj \quad \y = A \x + \e.
\end{equation}

\section{Characteristics of the ALM Algorithm}
Describe the two variants of the ALM algorithm

We need to define the following soft-thresholding operator for a
scalar $x$ and a scalar $\alpha \geq 0$:
\begin{equation}
\textup{shrink}(x,\alpha) = \textup{sign}(x)\cdot \max \{|x| - \alpha, 0\},
\end{equation}
In practice, this operator will be applied elementwise to a vector $\x$ with a single $\lambda$,
and will be notated as $\texup{shrink}(\x,\alpha).

Show Pseudocode for one variant
\subsection{Computational Complexity}
The Matrix-vector computions are O($mn$), and the vector-vector operations are O($m$), 
in terms of both computation cost and memory-bandwidth.
Therefore, assuming the iterative solver always takes a constant number of iterations,
the computational complexity of the overall algorithm is linear in the problem size.

@@

cuda cores, SIMD width, scheduling restrictions, bandwidth
\subsection{Solving a Single L1 minimization}
This section is about Victor's CUBLAS implementations.
Plot Solver Bandwidth in GB/s vs. Problem size in MB

@@

We summarize the entire ALM
algorithm as Algorithm~\ref{alg:alm}, where $\gamma$ denotes the
largest eigenvalue of the matrix $A^TA$. For the choice of parameter $\mu$, we take the same strategy as
in \cite{YangJ2009-pp} and set $\mu = 2m / \|\y\|_1$.
\begin{algorithm}[h]
\caption{\bf (Augmented Lagrange Multiplier Method for Global
Recognition)}
\begin{algorithmic}[1]
\STATE {\bf Input:} $\y \in \Re^m$, $A \in \Re^{m \times n}$,
$\x_1 = \mathbf{0}$, $\e_1 = \y$, $\blamda_1 =
\mathbf{0}$.
\WHILE{not converged ($k = 1,2,\ldots$)}
\STATE $\e_{k+1} = \textup{shrink}\left(\y - A\x_k +
\frac{1}{\mu}\blamda_k, \frac{1}{\mu}\right)$;
\STATE $t_1\leftarrow 1$, $\z_1 \leftarrow \x_k$, $\w_1 \leftarrow \x_k$;
\WHILE{not converged ($l = 1,2,\ldots$)}
\STATE $\w_{l+1} \leftarrow \textup{shrink}\left(\z_l +
\frac{1}{\gamma}A^T\left(\y - A\z_l - \e_{k+1} +
\frac{1}{\mu}\blamda_k\right), \frac{1}{\mu\gamma}\right)$;
\STATE $t_{l+1} \leftarrow \frac{1}{2}\left( 1 +
\sqrt{1+4t_l^2}\right)$;
\STATE $\z_{l+1} \leftarrow \w_{l+1} + \frac{t_l - 1}{t_{l+1}}(\w_{l+1} - \w_l)$;
\ENDWHILE
\STATE $\x_{k+1} \leftarrow \w_{l}$;
\STATE $\blamda_{k+1} \leftarrow \blamda_k + \mu (\y - A\x_{k+1} - \e_{k+1})$;
\ENDWHILE \STATE
{\bf Output:} $\x^* \leftarrow \x_k, \e^* \leftarrow \e_k$.
\end{algorithmic}
\label{alg:alm}
\end{algorithm}

\section{Conclusion}
...How lessons from this paper extend (or don't extend) to other similar problems in computer vision

...Reiterate how the appropriate hardware choice depends on the problem size.
